### 2014-09-29 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to colorbars

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/SMV_Pres_340_s}
\input{../Figures/colorbar_metric_pres}
\includegraphics[width=5.5in]{../Figures/SMV_Pres_343_s}
\input{../Figures/colorbar_metric_pres}
\caption{FDS simulated pressure contours, 2~s prior (top) and 1~s after (bottom) first rear basement window failure. The fire originated in the living room in the basement.}
\label{fig:smv_pressure}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity contours, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity vectors, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_velocity_vector}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature contours, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature vectors, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
\label{fig:smv_temperature_vector}
\end{figure}

@@

A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}. Although firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}. Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk. Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class III exposure~\cite{Donnelly2006}. Firefighters are at increased risk levels when encountering Class III exposure conditions for more than 5~minutes~\cite{Donnelly2006}. Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F). This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.

@@

% In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions. These conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}. Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground. In this case, the timing of the interior attack appears to have coincided with the failure time of the door. Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.

>>>>

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/SMV_Pres_340_s}
\input{../Figures/colorbar_metric_pres}
\includegraphics[width=5.5in]{../Figures/SMV_Pres_343_s}
\input{../Figures/colorbar_metric_pres}
\caption{FDS simulated pressure contours, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s). The fire originated in the living room in the basement.}
\label{fig:smv_pressure}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity_vector}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature_vector}
\end{figure}

@@

A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}. Although firefighters wear protective gear, gear only offers a finite amount of protection. The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}. Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}. Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk. Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class~III exposure~\cite{Donnelly2006}. Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}. Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F). This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.

@@

% In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions. These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}. Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground. In this case, the timing of the interior attack appears to have coincided with the failure time of the door. Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
